HO unification from object language to meta language

### 2024-02-15 main.tex
add example elpi->coq term

% syntax of coq terms in elpi
In particular, \coq terms are encoded following the following (very simplified)
data type:

\begin{elpicode}
  kind term type.
  type const gref -> term.
  type app list term -> term.
  type fun (term -> term) -> term.
  type prod (term -> term) -> term.
\end{elpicode}

Where a \coq constant is a gref\footnote{a gref is the opaque type for \coq
identifier in \elpi} inside the \elpiIn{const} constructor, the \coq application
is embedded in the \elpiIn{app} node, having the head and the arguments of the
application expressed as a list of terms. Lambda abstractions are translated
into the node \elpiIn{fun} binding a term to another term. Finally forall
quantification on the for \coqIn{~$\forall$~x,F} into \elpiIn{forall x\ F}.

@@

Let's take the following example:
\begin{tcolorboxSimple}
  \begin{tabular}{c|c}
    \begin{minipage}[c]{0.50\linewidth}
      \begin{coqcode}
        Instance forall_dec A (P: A ~$\to$~ Prop):
          Finite A ~$\to$~ 
          ~$\forall$~x, Decision (P x) ~$\to$~
          Decision (~$\forall$~x, P x).
      \end{coqcode}
    \end{minipage}
    &
    \begin{minipage}[c]{0.46\linewidth}
      \begin{elpicode}
        tc-Decision (prod x\ app[P, x]) :- 
          % premise for Finite A
          % premise for $\forall$x, Decision (P x)
      \end{elpicode}
    \end{minipage}
  \end{tabular}
\end{tcolorboxSimple}

@@

>>>>

% syntax of coq terms in elpi
In particular, \coq terms are encoded following the following (very simplified)
data type

% \begin{elpicode}
%   kind term type.
%   type const gref -> term.
%   type app list term -> term.
%   type fun (term -> term) -> term.
%   type prod (term -> term) -> term.
% \end{elpicode}

\begin{tcolorboxSimple}
  \begin{tabular}{c|c}
    \begin{minipage}[c]{0.50\linewidth}
      \begin{elpicode}
        kind term type.
        type const gref -> term.
        type app list term -> term.
        type fun (term -> term) -> term.
        type prod (term -> term) -> term.
      \end{elpicode}
    \end{minipage}
    &
    \begin{minipage}[c]{0.46\linewidth}
      \begin{textcode}
        Example:
        a        ==> const 0
        f a      ==> app[const f, const a]
        ~$\lambda$~x => x  ==> fun x\ x
        ~$\forall$x, F x~  ==> prod x\ app[F, x]
      \end{textcode}
    \end{minipage}
  \end{tabular}
\end{tcolorboxSimple}

\noindent where a \coq constant is a gref\footnote{a gref is the opaque type for \coq
identifier in \elpi} inside the \elpiIn{const} constructor, the \coq application
is embedded in the \elpiIn{app} node, having the head and the arguments of the
application expressed as a list of terms. Lambda abstractions are translated
into the node \elpiIn{fun} binding a term to another term. Finally forall
quantification on the for \coqIn{~$\forall$~x,F} into \elpiIn{forall x\ F}.

@@

Let's take the following example\footnote{taken from the \stdpp library}:
\begin{tcolorboxSimple}
  \begin{tabular}{c|c}
    \begin{minipage}[c]{0.50\linewidth}
      \begin{coqcode}
        Instance forall_dec A (P: A ~$\to$~ Prop):
          Finite A ~$\to$~ 
          ~$\forall$~x, Decision (P x) ~$\to$~
          Decision (~$\forall$~x, P x).
      \end{coqcode}
    \end{minipage}
    &
    \begin{minipage}[c]{0.46\linewidth}
      \begin{elpicode}
        tc-Decision (prod x\ app[P, x]) :- 
          % premise for Finite A
          % premise for $\forall$x, Decision (P x)
      \end{elpicode}
    \end{minipage}
  \end{tabular}
\end{tcolorboxSimple}

@@

An other example of unification failure in the
